% example
Considering a simple login screen feature inside an android application. A user can provide authentication credentials
in order to login. It's possible that a user enters wrong credentials, which in turn can be handled by the app by displaying
a short description of what went wrong, like an error message.
If the user then provides the wrong credentials more than three times, his user account could get locked. 
This also in some way must be expressed by the application.
He could also make use of the "Forgot Password" functionality. That could allow the user to navigate away from the application
into a browser window instead in order to reset the password.

% fixme{correct tables for finite statemachine}
% State Transition Table

It immediately becomes clear that there are already four possible states in which the application can be in.
A developer thus ends up with states * events possible states which must be considered and handled appropriately.

For example the application might be in the state of "logging in" and then a user tries to transition into
the event of "logging in" again, which might not be desirable.
 
The complexity for such a "simple" or at least standard feature grows linearly with the amount
of states and events that are introduced into the application.

Given that a project grows and more and more functionality is added to the codebase, the more 
important the state becomes and the harder it becomes to introduce state as an afterthought.


With the increasing states and events it becomes harder and harder to have a general overview of all
possible states.

In most cases an application communicates with other interfaces, such as a back-end or local database.
On mobile devices it's also often necessary to know the GPS status, whether mobile data is enabled or not, etc. 

A click of a user thus can cause many changes inside and outside of the application.
A developer must be aware of all the possible outcomes, react to them and save what has happened.

By increased application complexity the necessity to make sure the application behaves exactly
as expected in all cases increases. This property in software development is referred to a deterministic system, 
which states that a deterministic model always produce the same output from a given starting
condition or initial state. This is a desirable property because it makes it simpler to predict and reason about events and states
in which the application can be within.

The problem of opposite, nondeterministic software is thus that it makes the code less readable since
it's impractical to gloss over the code to determine the potential output of a function call.

Code readability becomes a vital part in codebases when they start growing in complexity and size. But also 
when they are being worked on by more people than just the person who initially wrote it.

Productive in writing code instead of deciphering other peoples codes it becomes essential.

A product of readability is another important property which is increased maintainability.
Maintainability ties into the notion of not having to rewrite parts of the codebase
that is not directly related to the functionality being added or modified.
% Problem End -- Summary

Thus far it can be summaries the problem to be that of maintainability, flexibility and readability.
These are basic concepts that unless respected have a domino-like side-effects 

And core to this problem is managing the applications state in a way that it can survive platform
restrictions like for example unexpected process death or in android specifically a configuration change
ie device rotation.

~~Once this basic login feature is implemented another problem emerges which is to add more functionality
like for example a 'protected view' which requires the user to be logged in 
this view should not be reachable from the 'logged out' state without
transition into 'logged in' state first.~~

Side-problems solved by solution to main problem

%* [x] Deterministic
%* [x] Open for extension, closed for modification

%* [x] Maintainability
%    * [x] Code readability

% # Problematic

% * Nondeterministic
% * Closed for extension, open for modification
% * Unreadable code
% * Unmaintainable code

\todo{mention reactive programming}
