\subsection{Problem}
\label{subsec:problem}

Today's applications has been increasing in complexity over the last few years.
Notably in the field of frontend development, the amount of functions has increased \cite{kevin2018}. The web development has transitioned from server rendered, 
page-reloading websites, to modern so called single page applications or SPA's.
The same applies to the mobile world: social networks, navigation, sharing and editing files together is a commonly demanded by the user.
A large part of applications are thus in exchange with APIs, interacting with local or external databases
and communicating with the underlying operating system itself (eg the periodic recording of the location via GPS or WiFi).
The challenge a developer faces is to come up with a general approach that bridges the gap between what the users sees, the source code
and the outside world - mainly: How to structure the source code. Ähnlich wie bei vielen Problemen die in der Softwareentwicklungen bestehen, existiert 
auch dieses seit geraumer Zeit und betrifft einen Großteil der Entwickler. Es is somit eine immer wiederkehrendes Problem. Daraus ensteht häufig das Bestreben, 
allgemeingültige Konzepte zu entwickeln, die dieser Problematik entgegenwirken und einen möglichen Lösungsweg aufzeigen. Die hier gesuchten Konzepte werden
als sogenannte "Entwurfsmuster" deklariert. Ihr zielt es, den Aufbau bzw. die Architektur von Quellcode so zu gestalten, dass er modular, flexibel und
wiederverwendbar ist. Zeitgleich wird der Entwickler dazu gewzungen einem Schema zu folgen und konistent zu arbeiten. Dies fördert die Qualität und
Wartbarkeit der Applikation. Über die Zeit haben sich viele Entwurfsmuster für die Strukturierung von Code innerhalb der Präsentationsschicht entwickelt. 
Dazu gehören unteranderem, nach "Erscheinungsjahr" sortiert: Model-View-Controller (MVC), Model-View-Presenter (MVP) Model-View-ViewModel (MVVM) und - relativ 
neu im Bunde - Model-View-Intent (MVI). Jedes der hier aufgezählten Muster dient dabei dem gleichen Zweck: Die strikte Trennung der Benutzeroberfläche von der ihr 
zugrundeliegenden (Geschäfts) Logik. Auch MVI bedient sicher dieser Idee.
Brought to life by André (Medeiros) Staltz, MVI encapsulates the interaction between the user and the application as a cycle, where the data flows unidirectionally.
It takes its inspiration from two conecepts: The original MVC as introduced by Trygve Reenskaug in 1979 and the often used javascript libraries redux and react. 
The idea of a cycle is based on the assumption that the output (e.g. a click) from a user resembles the input for the program. The program in turn produces an output 
which becomes the input for the user. This concept can be embodied as a chain of mathematical functions: f(g(a())) or view(model(intent(event))).
When the UI registers an event (e.g. a click) it will be passed to the intent functions as a parameter. The purpose of the intent-function is 
to translate the user generated event, as in what the user intended to do into something the application can understand and work with.
The model function then uses the output as its input. Its job is it to create a new model without changing the last one. That's what is called immutability.
Finally the view function receives the model as its input and takes care of rendering it (a visual representation of the model for the user). 
In order to achieve the cycle effect and the unidirectional data flow, MVI makes use of reactive programmming and the underlying "Observer Pattern".
\todo{why reactive, what does reactive solve for MVI?}
\todo{mention non-blocking UI?}
Given the description of MVI, the questions that arises are: What does an event look like? How is immutability achieved?
Since MVI does not have a Controller, Presenter or ViewModel: Where does the logic belong? And how is separation of concerns possible?
To summarize, it becomes a question of implementation. What does a developer have to do in order to implement or reap the benefits from this concept of MVI?